---
editor_options: 
  markdown: 
    wrap: 72
---

# Strategic Intent & Process of Creation {#sprint_2}

## Sprint Opening

Welcome to the second sprint of the CLIP. I hope that the fir

In this second sprint, the focus will be **Strategic Intent & Process of
Creation**.

::: {.infobox .goal data-latex="{.goal}"}

**Goal!**

Our webinar will be held on **April 30/2021** to officially launch the
Sprint II.

*Sprint dates: **From April 9 to April 29 / 2021***

It will be a synchronous session, so all CLT are expected to attend.
:::

In addition, a series of contents and activities are proposed to the CLT
to be completed during the sprint:

1.  Firstly, you will find **three conceptual videos** which are
    proposed to open the discussion on the three thematic pillars that
    constitute the construction of the Strategic Intent.

2.  Secondly, **two case experiences** from members of the consortium
    are shared. This way we can learn a little more about the experience
    of each of the CLT.

3.  Next, you will find the link to the **team workshop** of this
    sprint. The workshop should be completed before the end of the
    sprint (**April XX**).

4.  And finally, **complementary readings** are offered for those who
    would like to further explore the topics addressed in this sprint.

------------------------------------------------------------------------

## Conceptual Videos


### Background on Strategic intent

According to @Moultrie2007b, the design of an environment "enables the
development of unique capabilities, enables reconfiguration of
capabilities to changing demands, and supports synergies between
complementary assets". Hence, it is necessary to be conscious of which
kind of capabilities and assets are important to enable and how the
laboratory is strategically conceived around its context.

| Col1                  | Col2 |
|-----------------------|------|
| Strategic goals       |      |
| Symbolic goals        |      |
| Innovation efficiency |      |
|                       |      |
|                       |      |
: Strategic Intent of Innovation Environments Strategic goals

Looking to understand the degree of consciousness in which an innovation
laboratory is conceived... Some questions were presented according to
the levels of the grid to determine how managers reflect on specific
criteria from a strategic perspective. As for the strategic goals, we
found that the question seems understandable to respondents reflecting
on how they have foreseen


### Strategic Intent - Ferney

```{r}
knitr::include_url("https://www.youtube.com/embed/g6ukdHJxQoY")
```

Ferney 


### What is Proncess of Creation? - Laurent

```{r}
knitr::include_url(" ")
```

Laurent from Ashoka and 2811 shares an introduction to social innovation
and entrepreneurship.

------------------------------------------------------------------------

## Case Experiences

### Université de Lorraine -- Giovanny ARBELAEZ

```{r}
knitr::include_url(" ")
```

Professor Carola Calabuig shares his experience and vision on

------------------------------------------------------------------------

## Team Workshop 1

Here you can find for each University the link to the sprint II
workshop:

## Colombia {.unnumbered}

-   [Universidad de Caldas]()

-   [Universidad del Quindio]()

-   [Universidad de Manizales]()

-   [Universidad Tecnológica de Pereira]()

-   [Corporacion Universitaria Minuto de Dios]()

## Mexico {.unnumbered}

-   [Instituto Tecnológico y Estudios Superiores de Monterrey]()

-   [Universidad de Guadalajara]()

## Brazil {.unnumbered}

-   [Pontifícia Universidade Católica do Rio Grande do Sul]()

-   [Pontifícia Universidade Católica Do Paraná]()

-   [Universidade Católica de Pernambuco]()

## Let us know your comments

In this section, you can put any comments/questions or share your
thoughts and feedback about this sprint. To insert new text, use the
"Edit" button.

<iframe width="100%" height="300" src="https://hackmd.io/@fabbiocrux/CLIP-sprint-I" frameborder="0">

</iframe>
