# Process of Use & Outcomes {#sprint_4}

## Sprint Opening

This is the fourth sprint of the CLIP. Our attention now turns to the **Process of Use & Outcomes** of the Climate Labs.

::: {.infobox .goal data-latex="{.goal}"}
**GOAL**

The goal of sprint IV is:

> To round out your Climate Lab's strategic design and present your intent to all members of the Consortium.
>
> *Sprint dates: **From July 02 to September 02 / 2021***
:::

The opening webinar will be held on **July 02** to launch the Sprint IV. This is a synchronous session, so all CLT are expected to attend. As usual, a series of content and activities are proposed to the CLT to be completed during the course of the sprint:

1.  First, **two conceptual videos** are proposed to illustrate the process of use of innovation labs and the diversity on their outcomes.

2.  Second, as usual **two case experiences** from members of the consortium are shared. This way we can learn a little more about the experience of each of our partners.

3.  Finally, you will find the link to the **team workshop** of this sprint. The workshop must be completed prior to the tutoring session of this sprint (**August 27**).

------------------------------------------------------------------------

## Conceptual Videos

### Background on Process of Use & Outcomes

Innovation labs are forced to adapt to the changing conditions and this may lead to new or adapted uses of the space. The way innovation is actually supported, which creative activities are done within the lab, or to what degree the space really enables teamwork are some of the elements to take into consideration. But more importantly is to be sensitive to compare how much this has changed in comparison to the original intent and the process of creation. Being flexible but tracking those changes could lead to helpful insights to understand the role the lab.

The following are some of the aspects that should guide the process of use of an innovation lab [@osorio2019; @Moultrie2007b]:

+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+
| Criteria                    | Description                                                                                                                           |
+=============================+=======================================================================================================================================+
| Supporting Innovation       | The stage(s) of the innovation process in which the lab is actually used                                                              |
+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+
| Supporting Creativity       | The way in which the lab effectively supports creative activities                                                                     |
+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+
| Actual users & facilitators | The actual users that are welcome in the space. The actual degree of facilitation required for the activities conducted in/by the lab |
+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+
| Enabling teamwork           | The actual role of the space in enabling physical and virtual teamwork                                                                |
+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+
| Actual events               | The type of events that actually take place in the lab                                                                                |
+-----------------------------+---------------------------------------------------------------------------------------------------------------------------------------+

: Process of Use - Guiding set of criteria for Innovation Labs

Referring to innovation labs, it is naturally expected that their activity will result in some kind of innovation output. However, due to their intermediate nature, their results are not always easy to recognize or value. Beyond this, it is clear that the activity of innovation labs triggers a set of creative and innovation processes involving the community that ultimately lead to positive testimonials and compelling stories. Therefore, when referring to the outcomes of an innovation lab one should consider both its tangible and intangible results that are duplicable, new and useful in its context [@osorio2019; @Moultrie2007b].

| Criteria                        |
|---------------------------------|
| Tangible results                |
| Intangible results              |
| Realization of strategic intent |

: Outcomes - Guiding set of criteria for Innovation Labs

### The Green FabLab Project - Fabio Cruz

```{r}
knitr::include_url("https://www.youtube.com/embed/S83IliOQ9tc")
```

Fabio Cruz, research associate at the University of Lorraine presents the case of Green FabLab, a research project dedicated to the creation of a local and open source plastic recycling process for a circular economy. To know more about this project you can have a look to the paper [@roux-marchand2020].

### LabCidades: The Community Garden - Rafael Camargo & André Turbay

```{r}
knitr::include_url("https://www.youtube.com/embed/GHU2JULU5qg")
```

The Community Garden brought together several actors from the neighborhood that includes PUCPR. From the dream of a resident of the neighborhood, to transform an area that served as a waste deposit into a space that would contribute to the community. As a result of this initiative, several actors were connected, such as a local daycare center, collectors of recyclables, and the PUCPR itself, through LabCidades and the Curos de Agronomia. This video explains how this transformation took place.

------------------------------------------------------------------------

## Case Experience

### Université de Lorraine -- Mauricio Camargo

```{r}
knitr::include_url("https://www.youtube.com/embed/iBOAZllc7bQ")
```

Professor Mauricio Camargo, Director of the Research Institute for Research in Innovation Processes - ERPI and Professor at the School of Innovation - ENSGSI explains the role of the Lorraine Fab Living Lab - LF2L at the Université de Lorraine.

------------------------------------------------------------------------

## Team Workshop 5 - Pitch your Climate Lab!

The purpose of this workshop is for you to round-up the strategic design of your Climate Lab and be ready to communicate your intent to your partners and stakeholders. Therefore, the main task for you during this fourth sprint is to prepare [a pitch to present your Climate Lab in 3 minutes]{.ul}. The following are the main steps that we are going to follow:

1.  **Prepare your pitch!**

    -   Round-up the strategic design of your Climate Labs. This means that you should have finished all the precedents workshops so you can have all the insights to feed your pitch.

    -   Based on all the previous work, collectively identify your value, your ambition, your strengths and your expected tangible and intangible results (environmental impact, social impact...).

    -   Any pitch must be tailored to the audience. Identify what emotions you want to generate: (i) create a connection with your audience to establish shared values or build communion, (ii) foster collaboration by getting the audience to take action or side with you, or (iii) generate awareness through education and be informative.

2.  **Let's test your pitch!**

    -   During the mentoring session ([August 27]{.ul}) each one of the CLT will present their Climate Lab to all members of consortium.

    -   You will receive feedback from mentors and all the Climate Lab community.

3.  **Present your pitch to the Climate Lab External Committee!**

    -   Reflect on the feedback received from your peers and adjust your pitch

    -   A special event is being prepared for the opening of Sprint 5 ([September 03]{.ul}) where all CLT are invited to present their Climate Lab in 3 minutes to the External Committee. Be ready!

Here we share with you some tips for making an impactful pitch:

-   Identify what type of pitch you want to use. You can mix types, but be as clear as possible.

    -   **Tweet Pitch:** respond to the questions: What? How? Why? answer a question: what does the Climate Lab do?

    -   **Pitch to investors:** have a structure with key elements, why they are going to leave their money in your lab.

    -   **Pitch to partners:** present the purpose of your lab, show what are the advantages of collaborating with your lab. Ask all team members why they want to work on this climate lab project.

    -   **Sales pitch:** convince your potential clients to trust in your lab initiative, to participate in it. Present how your Climate Lab will be useful in their life.

-   Find 10 words that best represent your Climate Lab. Choose 10 words that you think are the most meaningful to share about your lab.

-   The key part of a speech:

    -   The first sentence of a pitch is the most important. It must grab attention and the audience must understand the purpose of your project.  

    -   Identify what problem you are going to address. State the emotions associated with that problem.

    -   Present the results and what you will do in your lab.

-   Finally, training is extremely important. Your pitch will become clearer with practice.

***Tips based on:***

-   *Morlet, C. & Deloupy, B. (2018). Outil 11. Générez un impact en deux minutes : le pitch. Dans : , C. Morlet & B. Deloupy (Dir), La boîte à outils du Speaker-Conférencier (pp. 44-47). Paris: Dunod.*

-   *Morgan, W. R., & Wright, E. S. (2021). Ten simple rules for hitting a home run with your elevator pitch. PLoS Computational Biology, 17(3), 1--5. <https://doi.org/10.1371/JOURNAL.PCBI.1008756>*

-   *EF Venturas, (2021) Aprende cómo construir un pitch ganador*
